High geomagnetic field intensity recorded by anorthosite xenoliths requires a vigorous late Mesoproterozoic geodynamo

### 2022-02-11 PNAS_manuscript/Supporting Info.tex
Updates from Overleaf

% \clearpage

@@

\caption{\footnotesize{Summary paleointensity results for specimens that passed our selection. Paleointensity results for specimens that passed quality criteria. B$_{anc}$ is the calculated ancient field intensity over the chosen temperature interval in $\mu$T. T$_{min}$ and T$_{max}$ indicate the temperature interval over which the best fit for paleointensity was defined. N is the number of steps used within the selected interval for paleointensity determination. FRAC is the fraction of remanence. NpTRM shows the number of pTRM checks within the selected interval for paleointensity determination. $\beta$ is the scatter parameter.  GAP-MAX is the maximum magnetization gap between two adjacent steps. MAD is the maximum angle of deviation. DANG is the deviation angle. SCAT is the scatter parameter. Paleolatitude is calculated from the inclination values reported in \cite{Zhang2021b}. $\gamma$ is the gamma statistic that measures the angle between the last pTRM step used for paleointensity determination and the applied field direction. V(A)DM is the virtual (axial) dipole moment reported in $10^{21}$Am$^2$ (ZAm$^2$). }}

@@

>>>>

\begin{figure*}[h!]
\noindent\includegraphics[width=0.9\textwidth]{Cenozoic_resample.pdf}
\centering
\caption{\footnotesize{A) Summary plot of individual specimen absolute paleointensity results (square symbols) and their averages and standard deviations at site level (black bars with grey uncertainty boxes). All results are corrected for cooling rate with a factor of 0.74. Each `AX' site is an individual anorthosite xenolith within the Beaver River diabase. The sites with successful experiments come from 3 regions which would have cooled at distinct times yielding similar estimates within the each region with differences between regions. B) Specimen level means calculated for these regions are compared to the distribution of intensities calculated from a paleomagnetic axial dipole moment model for the past 2 million years (PADM2M; \citealp{Ziegler2011a}) at the latitude corresponding to the paleolatitude of study region (22\textdegree N). C) The mean of the 3 regional means is compared to means calculated from 3 random values drawn from the PADM2M model \cite{Ziegler2011a}. The distribution represents a total of 10,000 iterations of taking 3 random draws and calculating the mean.}}
\label{fig:Cenozoic_PINT}
\end{figure*}

@@

\caption{\footnotesize{Specimen paleointensity results that passed our selection. Paleointensity results for specimens that passed quality criteria. B$_{anc}$ is the calculated ancient field intensity over the chosen temperature interval in $\mu$T. T$_{min}$ and T$_{max}$ indicate the temperature interval over which the best fit for paleointensity was defined. N is the number of steps used within the selected interval for paleointensity determination. FRAC is the fraction of remanence. NpTRM shows the number of pTRM checks within the selected interval for paleointensity determination. $\beta$ is the scatter parameter.  GAP-MAX is the maximum magnetization gap between two adjacent steps. MAD is the maximum angle of deviation. DANG is the deviation angle. SCAT is the scatter parameter. Paleolatitude is calculated from the inclination values reported in \cite{Zhang2021b}. $\gamma$ is the gamma statistic that measures the angle between the last pTRM step used for paleointensity determination and the applied field direction. V(A)DM is the virtual (axial) dipole moment reported in $10^{21}$Am$^2$ (ZAm$^2$). }}

@@

\begin{table}[]
\centering
\caption{\footnotesize{Summary paleointensity result statistics at site-level, region-level, and overall mean. The statistics names are the same as in Table \ref{tab:PINT_result}}. n represents the total number of specimen- or site-level results used for calculating mean values. Site-level means for AX6, AX8, AX10, AX11, AX12, AX13, AX16 are calculated based on specimen results. Regional means for Carlton Peak, Kennedy Creek, and Silver Bay are calculated by grouping specimen results from AX6 and AX8 and AX10, AX11 and AX13, AX12 and AX16, respectively. Overall site mean values are calculated using all site level results in this table. Overall region mean values are calculated using all regional mean results in this table. }
\begin{tabular}{cccccccccc}
\hline
Group                & B$_{anc}$ & n  & FRAC & GAP-MAX & MAD ($^\circ$) & DANG ($^\circ$) & Paleolatitude & $\gamma$ & VDM (ZAm$^2$) \\
\hline
AX6                 & 30.33     & 3  & 0.69 & 0.13    & 3.55           & 2.66            & 21.97         & 2.63     & 48.76         \\
AX8                 & 52.4      & 3  & 0.66 & 0.17    & 4.28           & 2.15            & 22.98         & 7.3      & 83.14         \\
AX10                & 46.82     & 3  & 0.7  & 0.23    & 4.98           & 2.14            & 20.37         & 6.1      & 76.81         \\
AX12                & 38.1      & 6  & 0.75 & 0.22    & 3.26           & 2.53            & 35.73         & 5.98     & 51.31         \\
AX16                & 44.15     & 11 & 0.68 & 0.19    & 4.19           & 1.96            & 30.08         & 3.97     & 63.87         \\
AX11                & 73.34     & 7  & 0.68 & 0.19    & 3.85           & 1.82            & 19.43         & 6.63     & 121.73        \\
AX13                & 76.63     & 7  & 0.73 & 0.2     & 5.7            & 1.67            & 19.36         & 5        & 127.29        \\
Carlton Peak        & 43.18     & 9  & 0.68 & 0.17    & 4.27           & 2.32            & 21.77         & 5.34     & 69.57         \\
Kennedy Creek       & 74.98     & 14 & 0.7  & 0.2     & 4.78           & 1.74            & 19.4          & 5.81     & 124.51        \\
Silver Bay          & 42.02     & 17 & 0.71 & 0.2     & 3.86           & 2.16            & 32.07         & 4.68     & 59.44         \\
overall site mean   & 51.68     & 40 & 0.7  & 0.19    & 4.26           & 2.13            & 24.27         & 5.37     & 81.84         \\
overall region mean & 53.39     & 40 & 0.7  & 0.19    & 4.3            & 2.07            & 24.41         & 5.28     & 84.51        \\
\hline
\end{tabular}
\end{table}
